\documentclass{project}
\begin{document}
\section{Personal Report}
\subsection{Mike Steel}
\paragraph{Project Outset}
From the outset our project team has been clearly organised into one group who are more comfortable with code and one group who are more comfortable with documentation, this has been helpful during each stage of development, as it was defined early on who would be best at each task. By giving each documenter a specific part of the code to document it allowed them to get to know the person working on that part of the code, as well as get to grips with how that part of the program would function and allow for documentation. As you can probably tell from what I have mentioned so far, I was a member of the documenting team, and had little part in the actual coding of the program, however, even though the documenters and the coders worked relatively seperately on the different parts of the project, when we needed to consult with each other over designs and the like we worked together well, and as a whole the group itself worked together well as a single unit completing each necessary part of the project.
\paragraph{Project Outcome}
By the time it came to implementation and testing week the group were used to working together enough that the final implementation of the project and especially the testing worked out very well. Most people turned up when required so that documentation was completed between testing phases, and the optimum amount of work was done for the time that we had. If there had not been the network problems and last minute project specification changes then we would have most certainly finished all functional requirements of the project, and it is a shame that those problems that we encountered were out of our control. Overall, the final outcome of the project is something that I am very happy with, and would work with the same group again any time. We all did what needed to be done, and helped each other out as well as included everyone in decision making.
\paragraph{Personal Reflection}
I have enjoyed this project very much, and even though at times the work load has been more than I was expecting I know that some group members have worked on this project for far longer and harder than I would ever be able to make myself do, and I am truly impressed by some of the levels of work that some group members have put into this project. The experience has certainly prepared me for future group work, both in future university projects and in the world of work. This project has made me a more able group member, and has allowed me to experience every stage of an industry-worthy project. Therefore, I am now a more competant and experienced worker, and ready to do more work within groups in the future.
\label{thelastpage}
\end{document}