\documentclass{project}
\usepackage[pdfauthor={C. P. Marriott},pdftitle={Software Engineering Group Project, Project Plan},pdftex]{hyperref}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}
\hypersetup{colorlinks=false,pdfborder={0 0 0}}
\begin{document}
\title{Software Development Life cycle}
\subtitle{End of project report}
\author{Tom Reed, Matt Whitmore, Dave Clark, Silhab Csoma, Mike Steel, Chris 'Tux' Lloyd, Aleksandra Badyda, Samuel Jackson, Chris Marriott}
\shorttitle{End report}
\version{1}
\status{draft}
\date{2013-01-30}
\configref{SE.17.DS.01}
\maketitle
\tableofcontents
\newpage
\section{Management Summary}
This should sum up in one page what the project achieved (what parts of the program
work and what parts do not; which documents are in a good state and which are not), what difficulties stood in
the way of project completion and how they were overcome, and how well the team performed.
\section{Historical account of project}
This should outline the main events over the lifetime of the project, and how
the project team acted to produce a plan and to deliver a product within a constrained lifetime. This should take
no more than two pages of A4.

\section{Final State of project}
This should give a summary of which parts of the project are perceived as correct and
which are not. It is as well to be as accurate as possible here - more marks will be deducted for problems that are
not declared but are detected by the markers than for problems that are declared in the final report. As well as
missing or erroneous features in the software, known problems with documents should be included here.

\section{Performance of each team member}
The project leader should write a half page description of the duties and
performance of each group member, including the group leaders themselves. This should be agreed with the
group member if possible, and it should state whether agreement was reached, and if not, should give an
explanation why not.

\section{Critical evaluation of the team and project}
This should be no more than a page in length and should address
the following subjects:
\begin{itemize}
	\item How did the team perform as a whole, and how could that have been improved?
	\item How could the project have been improved?
	\item What were the most important lessons learned about software projects and about working in teams?
\end{itemize}
\clearpage
\addcontentsline{toc}{section}{REFERENCES}
\begin{thebibliography}{5}
\bibitem{} \emph{N/A}
\end{thebibliography}
\clearpage
\addcontentsline{toc}{section}{DOCUMENT HISTORY}
\section*{DOCUMENT HISTORY}
\begin{tabular}{|l | l | l | l | l |}
\hline
Version & CCF No. & Date & Changes made to Document & Changed by \\
\hline
1.0 & N/A & 2013-01-30 & Initial creation & dac26 \\
\hline
\end{tabular}
\label{thelastpage}
\end{document}